The thin blue line:\\what protects my Android device?

### 2015-03-31 securityupdates.tex
add a possible todo about 95% confidence intervals

Where possible we indicate the uncertainty in our results by presenting them $\pm$ one standard deviation and give results to 3 significant figures, this occasionally results in `$\pm\, 0$' when the standard deviation is small.
This technique cannot account for systematic errors which we explore in \S\ref{sec:representative}.

>>>>

Where possible we indicate the uncertainty in our results by presenting them $\pm$ one standard deviation and give results to 3 significant figures, this occasionally results in `$\pm\, 0$' when the standard deviation is small.\todolater{Do we want to use the 95 percentile instead}
This technique cannot account for systematic errors which we explore in \S\ref{sec:representative}.
